\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-06-20 popl-2019-journal-v/discussion.tex
[POPLjv] Discussion of overlay semantics and back-translation

  % TODO new paragraph: Machine checked proof. MANY details, any future work should be machine checked?

  % TODO new subsection on construction of overlay semantics:
  % If we don't, we will have to come up with new syntax. Further, say we had
  % introduced new instruction, how would we do the back translation? We would not
  % be able to tell whether a series of instructions came from a call or a series of
  % instructions that just look like a call. With this approach everything that
  % looks like a call is a call. The back translation is simply the identity making
  % things a lot easier.

\end{jversion}

>>>>

  % TODO new paragraph: Machine checked proof. MANY details, any future work should be machine checked?
  One challenge in full-abstraction proofs is to relate the translation of program to the program it was translated from.
  Such a relation is often expressed as a back-translation  \citep{devriese_modular_2017}, i.e.\ a translation from the target language to the source language.
  When we use an overlay semantics, the back-translation becomes trivial because the source and target language are syntactically the same, so the identity can be used as the back-translation.
  If we have native call and return instructions in the source language, then the source language would be different from the target language, and we would have to use a non-trivial back-translation.
  Specifically, the back-translation would need to distinguish sequences of instructions that is the translation of a call from sequences of instructions that just look like a call.
  With overlay semantics, this is not a concern because everything that looks like a call is interpreted as a call.
\end{jversion}
